M07-SVM

### 2020-10-19 DATA622/M07-svm.rmd
Updated M07-SVM

#Load input data heart.csv and ecoli.csv
```{r MainCode}
unixpath<-"/home/data/ML.Data/heart.csv"
unixecolipath<-"/home/data/ML.Data/ecoli.csv"
path<-"c://Users/rk215/Data/heart.csv"
ecolipath<-"c://Users/rk215/Data/ecoli.csv"
heart<-read.csv(path,header=TRUE,sep=',',stringsAsFactors=FALSE)
ecoli<-read.csv(ecolipath,head=T,sep=',',stringsAsFactors=F)

>>>>

#Load input data heart.csv and ecoli.csv
```{r MainCode}
unixpath<-"heart.csv"
unixecolipath<-"ecoli.csv"
path<-"heart.csv"
ecolipath<-"ecoli.csv"
heart<-read.csv(path,header=TRUE,sep=',',stringsAsFactors=FALSE)
ecoli<-read.csv(ecolipath,head=T,sep=',',stringsAsFactors=F)
